%%%% Proceedings format for most of ACM conferences (with the exceptions listed below) and all ICPS volumes.
\documentclass[sigconf]{acmart}
%%%% As of March 2017, [siggraph] is no longer used. Please use sigconf (above) for SIGGRAPH conferences.

%%%% Proceedings format for SIGPLAN conferences 
% \documentclass[sigplan, anonymous, review]{acmart}

%%%% Proceedings format for SIGCHI conferences
% \documentclass[sigchi, review]{acmart}

%%%% To use the SIGCHI extended abstract template, please visit
% https://www.overleaf.com/read/zzzfqvkmrfzn


\usepackage{booktabs} % For formal tables


% Copyright
% \setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
\acmDOI{10.475/123_4}

% ISBN
\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[DAC'19]{ Design Automation conference}{June 2019}{
  LasVegas, NV USA}
\acmYear{2019}
\copyrightyear{2019}


% These commands are optional
%\acmBooktitle{Transactions of the ACM Woodstock conference}
\editor{Jennifer B. Sartor}
\editor{Theo D'Hondt}
\editor{Wolfgang De Meuter}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{physics}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage[euler]{textgreek}
\usetikzlibrary{shapes,shapes.geometric,arrows,fit,calc,positioning,automata}
\usepackage{textgreek,stackengine}
\usetikzlibrary{arrows}
\usepackage[T1]{fontenc}
\usetikzlibrary{shapes.geometric}
\usetikzlibrary{decorations.text,calc,arrows.meta}
%\usetikzlibrary{positioning, paths.ortho}
\usetikzlibrary{arrows.meta,arrows,positioning,fit,calc}
\usetikzlibrary{automata}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\DeclareRobustCommand\grdot[1]{%
	\leavevmode
	\vbox{
		\offinterlineskip
		\ialign{%
			##\cr
			\hidewidth\.{}\hidewidth\cr
			\noalign{\kern-1ex}
			#1\cr
		}
	}%
}
\DeclareRobustCommand\grcap[1]{%
	\leavevmode
	\vbox{
		\offinterlineskip
		\ialign{%
			##\cr
			\hidewidth\^{}\hidewidth\cr
			\noalign{\kern-1ex}
			#1\cr
		}
	}%
}
\DeclareRobustCommand\grdash[1]{%
	\leavevmode
	\vbox{
		\offinterlineskip
		\ialign{%
			##\cr
			\hidewidth\'{}\hidewidth\cr
			\noalign{\kern-1ex}
			#1\cr
		}
	}%
}
\makeatletter
\newcommand*{\MoveFitHeight}[1]{%
	\pgfmathsetlengthmacro\fit@inner@sep{%
		\pgfkeysvalueof{/pgf/inner xsep}%
	}%
	\pgfmathsetlengthmacro\fit@text@height{%
		\tikz@text@height
	}%
	\kern-\fit@inner@sep\relax
	\raisebox{\fit@text@height}[0pt][0pt]{#1}%
}

\begin{document}
\title{Model Based design and validation of Cyber-physical Systems}
\titlenote{Produces the permission block, and
  copyright information}
\subtitle{Extended Abstract}
\subtitlenote{The full version of the author's guide is available as
  \texttt{acmart.pdf} document}

\author{Charles Palmer}
\affiliation{%
  \institution{Palmer Research Laboratories}
  \streetaddress{8600 Datapoint Drive}
  \city{San Antonio}
  \state{Texas}
  \postcode{78229}}
\email{cpalmer@prl.com}

\author{John Smith}
\affiliation{\institution{The Th{\o}rv{\"a}ld Group}}
\email{jsmith@affiliation.org}

\author{Julius P.~Kumquat}
\affiliation{\institution{The Kumquat Consortium}}
\email{jpkumquat@consortium.net}

% The default list of authors is too long for headers.
%\renewcommand{\shortauthors}{B. Trovato et al.}


\begin{abstract}
Real time correctness of cyber physical systems has been a challenge so far. There have been many implementations to justify the controller correctness in real time but all of these have not been meticulously successful. One reason is, the plant models are mostly realized in software, which cannot handle realtime problems like jitters,skews and real world timing issues. Simulations of such systems rely on level crossings and ways applied to check them are fraught with inefficiencies and inaccuracies. Consequently, these implementations do not guarantee the timing and functional correctness of the controllers. The proposed methodology uses model based design technique, followed by hardware in loop simulation and tries to address these shortcomings. A well known formal model for cyber physical systems based on hybrid input output Automata (HIOA) has been used as the main vehicle. The HIOA comprises of a plant as a physical system, and a controller interfacing to it. To verify functional correctness of such systems in hardware we use MITL specifications as assertions and chose specific lockstep value as clock period such that it is robust enough to satisfy all MITL specifications for a given design. Hence, the proposed approach enables any cyber physical system to be modeled into hardware effectively, taking care of jitter, skew etc. and ensures controller correctness.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}


\keywords{SVA, Cyber Physical Systems, Hybrid System, Numerical Integration, MITL, MTL.}


\maketitle
\title{Model Based design and validation of Cyber-physical Systems}

\input{samplebody-conf}

\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-bibliography}

\end{document}

